Topological Equivariant Artist Model for Visualization Library Architecture

### 2021-11-26 paper/main.tex
pullback figure

of sheaf functors 
\begin{equation}
  \label{eq:artist:sheaf_map}
  \vartistc: \sheafc_{\vindexc^*}(\dtotalc) \rightarrow \sheafc_{\vartistc}(\gtotalc)
\end{equation}
where each sheaf is a map from an open set in the graphic base space $\opensetg \subset \gbase$ into a set of sections of a fiber bundle over that open set. As defined in \autoref{eq:related-work:equivariance:natural-transform}, the artist is a natural transformation. The artist has two components, a sheaf morphism $\vartist_{\openset}$ and a morphism $\vartist_{\Gamma}$ between sets of sections.

\begin{equation}
  \label{eq:artist:artist_gamma}
\end{equation}

As illustrated in \autoref{eq:artist:morphism-of-sheaf-data}, the morphism between data sheaves is $\dfunc$. By definition of a natural transform, the following diagram commutes

>>>>

of sheaf functors 
\begin{equation}
  \label{eq:artist:sheaf_map}
  \vartistc: \sheafc_{\vindexc^*}(\dtotalc) \rightarrow \sheafc_{\vartistc}(\gtotalc)
\end{equation}
where each sheaf is a map from an open set in the graphic base space $\opensetg \subset \gbase$ into a set of sections of a fiber bundle over that open set. As defined in \autoref{eq:related-work:equivariance:natural-transform}, the artist is a natural transformation. Following from \autoref{eq:related-work:equivariance:natural_transform_commute}, the artist specifies that there are compatible inclusion maps in the data and graphic spaces 
\begin{equation}
  \label{eq:artist:inclusion_morphisms}
  \begin{tikzcd}
    {\Gamma(\opensetc_1, \dtotalc)} \arrow[dd, "\vartistc_{\opensetc_1}"'] &                                                                                                                                   &  &                                                                                                         & {\Gamma(\opensetc_2,\dtotal)} \arrow[dd, "\vartistc_{\opensetc_2}"] \arrow[llll, "\iota^*"', hook'] \\
                                                                           & \opensetc_1 \arrow[lu, "\sheafc_{\vindex^*}" description] \arrow[ld, "\sheafc_{\vartistc}" description] \arrow[rr, "\iota", hook] &  & \opensetc_2 \arrow[ru, "\sheafc_{\vindex^*}" description] \arrow[rd, "\sheafc_{\vartistc}" description] & \\
    {\Gamma(\opensetc_1,\gtotalc)} & &  && {\Gamma(\opensetc_2,\gtotalc)} \arrow[llll, "\iota^*", hook']                                       
    \end{tikzcd}
\end{equation}

In \autoref{eq:artist:morphism-of-sheaf-data}, $\dfuncc$ was introduced as a morphism between sheaf functors $\sheafc^{\vindex^*}$. Since the artist is a functor $\vartist: \sheafc^{\vindex^*} \rightarrow \sheaf_{\vartist}$, it follows from \autoref{eq:related-work:equivariance:functor_diagram} that 
\begin{equation}
  \begin{tikzcd}
    \sheafc_{\vindex^{*}} \arrow[d, "\dfuncc"'] \arrow[r, "\vartistc"] & \sheafc_{\vartist} \arrow[d, "\dfuncc^{\prime} \coloneqq\vartist(\dfuncc)"] \\
    \sheafc_{\vindex^{*}} \arrow[r, "\vartistc"']                      & \sheafc_{\vartist}                                                         
    \end{tikzcd}
\end{equation}
an arbitrary morphism $\dfunc$ on the data sheaf has a compatible morphism $\dfunc^{\prime}$ on the graphic sheaf.
